
---
title: "Getting Started with df2cypher"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with df2cypher}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(df2cypher)
```

## Introduction

The `df2cypher` package provides functions to help you convert R data frames into Cypher statements suitable for importing into a Neo4j graph database.

This vignette walks through a basic example to demonstrate how to convert node and relationship data frames into Cypher statements and preview them.

## Creating Nodes

Start by creating a sample data frame for nodes:

```{r nodes}
nodes_df <- data.frame(
  id = c("1", "2", "3"),
  name = c("Alice", "Bob", "Charlie"),
  age = c(34, 29, 41),
  stringsAsFactors = FALSE
)

node_statements <- df_to_cypher_node(
  df = nodes_df,
  label = "Person",
  id_column = "id"
)

preview_cypher(node_statements)
```

## Creating Relationships

Now, create a data frame for relationships between the nodes:

```{r relationships}
rel_df <- data.frame(
  source = c("1", "2"),
  target = c("2", "3"),
  since = c(2020, 2021),
  stringsAsFactors = FALSE
)

rel_statements <- df_to_cypher_relationship(
  df = rel_df,
  from_col = "source",
  to_col = "target",
  rel_type = "KNOWS",
  direction = "out"
)

preview_cypher(rel_statements)
```

## Conclusion

You now have a set of Cypher statements for both nodes and relationships. These can be exported to a file and imported into Neo4j.

```{r write-cypher}
tmp <- tempfile(fileext = ".cypher")
write_cypher_file(c(node_statements, rel_statements), tmp)
cat("Cypher statements written to:", tmp)
```
