
---
title: "Advanced Usage of df2cypher"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced Usage of df2cypher}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(df2cypher)
```

## Introduction

This advanced vignette explores more complex usage of the `df2cypher` package, including support for `MERGE`, setting `ON CREATE` and `ON MATCH` properties, and handling undirected relationships.

## Node Example with Multiple Labels and Data Normalization

```{r advanced-nodes}
nodes_df <- data.frame(
  node_id = c("n1", "n2", "n3"),
  fullName = c("Diana Prince", "Bruce Wayne", "Clark Kent"),
  role = c("Analyst", "Manager", "Engineer"),
  stringsAsFactors = FALSE
)

# Normalize columns (e.g., snake_case)
nodes_df <- normalize_column_names(nodes_df)

node_statements <- df_to_cypher_node(
  df = nodes_df,
  label = "Employee",
  id_column = "node_id"
)

preview_cypher(node_statements)
```

## Using MERGE and ON CREATE/ON MATCH for Relationships

```{r advanced-relationships}
rel_df <- data.frame(
  source = c("n1", "n2"),
  target = c("n2", "n3"),
  trust_level = c("low", "high"),
  stringsAsFactors = FALSE
)

rel_statements <- df_to_cypher_relationship(
  df = rel_df,
  from_col = "source",
  to_col = "target",
  rel_type = "TRUSTS",
  direction = "out",
  use_merge = TRUE,
  on_create = list(created = "2023-01-01"),
  on_match = list(updated = "2024-01-01")
)

preview_cypher(rel_statements)
```

## Undirected Relationship Example

```{r undirected}
undirected_df <- data.frame(
  source = c("n1"),
  target = c("n3"),
  stringsAsFactors = FALSE
)

undirected_statements <- df_to_cypher_relationship(
  df = undirected_df,
  from_col = "source",
  to_col = "target",
  rel_type = "COLLABORATES_WITH",
  direction = "undirected"
)

preview_cypher(undirected_statements)
```

## Writing All Statements to File

```{r write-advanced}
all_statements <- c(node_statements, rel_statements, undirected_statements)
tmp <- tempfile(fileext = ".cypher")
write_cypher_file(all_statements, tmp)
cat("Cypher statements written to:", tmp)
```

## Summary

This vignette demonstrated:
- Using `normalize_column_names` for schema consistency
- `MERGE` for idempotent writes
- `ON CREATE` and `ON MATCH` clauses
- Undirected relationship handling

Use these tools to enrich your Neo4j data model cleanly and efficiently.
